Quality Metrics for SKOS Vocabularies

### 2012-03-12 analysis.tex
added results for lc metrics

\begin{table}[h]
\caption{Analyzed vocabularies}
\begin{tabular}{lp{5cm}cccccc}
\textbf{Domain} & \textbf{Vocabulary} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Lexical Rel.}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
\toprule
Media & Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
\hline
Science & Geonames Ontology & 671 & 671 & 0 & 671 & 9 & 0 \\
\hline
& Medical Subject Headings (MeSH) & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
\hline
& Peroxisome Knowledge Base & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
\hline
Government & Eurovoc & 6797 & 457788 & 18491 & 15512 & 128 & 0 \\
\hline
& Integrated Public Sector Vocabulary (IPSV) & 4732 & 7945 & 13843 & 4483 & 3 & 0 \\
\hline
Publications & Agrovoc & 31993 & 572138 & 63936 & 32043 & 1 & 0 \\
\hline
& DBpedia Categories & 743410 & 740352 & 1490316 & 0 & 0 & 0 \\
\hline
& University of Southampton Pressinfo & 1125 & 0 & 0 & 0 & 0 & 0 \\
\hline
& New York Times People & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
\hline
& Library of Congress Subject Headings (LCSH) & 459182 & 746076 & 595754 & 815816 & 19 & 0 \\
\hline
Cross-domain & Meketre & 422 & 569 & 1698 & 6 & 2 & 0 \\
\hline
Economy & Thesaurus for Economics (STW) & 6524 & 31189 & 57907 & 6531 & 1 & 0 \\
\hline
& North American Industry Classification System (NAICS) & 4175 & 0 & 8684 & 2235 & 1 & 0 \\
\hline
Military & Thesaurus Landesverteidigungsakademie (LVAk) & 13411 & 17250 & 16346 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\label{vocabs}
\end{table}

@@

\todo{CM}{Add the result table, with one row for the lc metric.}

>>>>

\begin{table}[h]
\caption{Analyzed vocabularies}
\begin{tabular}{lp{4.7cm}cccccc}
\textbf{Domain} & \textbf{Vocabulary} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Lexical Rel.}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
\toprule
Media & Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
\hline
Science & Geonames Ontology & 671 & 671 & 0 & 671 & 9 & 0 \\
\hline
& Medical Subject Headings (MeSH) & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
\hline
& Peroxisome Knowledge Base (PXV) & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
\hline
Government & Eurovoc & 6797 & 457788 & 18491 & 15512 & 128 & 0 \\
\hline
& Integrated Public Sector Vocabulary (IPSV) & 4732 & 7945 & 13843 & 4483 & 3 & 0 \\
\hline
Publications & Agrovoc & 31993 & 572138 & 63936 & 32043 & 1 & 0 \\
\hline
& DBpedia Categories & 743410 & 740352 & 1490316 & 0 & 0 & 0 \\
\hline
& University of Southampton Pressinfo & 1125 & 0 & 0 & 0 & 0 & 0 \\
\hline
& New York Times People (NYTP) & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
\hline
& Library of Congress Subject Headings (LCSH) & 459182 & 746076 & 595754 & 815816 & 19 & 0 \\
\hline
Cross-domain & Meketre & 422 & 569 & 1698 & 6 & 2 & 0 \\
\hline
Economy & Thesaurus for Economics (STW) & 6524 & 31189 & 57907 & 6531 & 1 & 0 \\
\hline
& North American Industry Classification System (NAICS) & 4175 & 0 & 8684 & 2235 & 1 & 0 \\
\hline
Military & Thesaurus Landesverteidigungsakademie (LVAk) & 13411 & 17250 & 16346 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\label{vocabs}
\end{table}

@@

\begin{table}[h]
\caption{Results of the proposed metrics}
\begin{tabular}{lccccccccccccccc}
\textbf{Metric} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
\toprule
Loose Concepts & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 77062 & 1125 & 0 & 0 & 0 & 0 & 0 & 21 \\
\bottomrule
\end{tabular}
\end{table}
